Rotations and Insecticide Resistance initial plots

### 2017-11-22 inst/documents/rotations_notes.Rmd
added initial no_r_below_start to stop resistance declining below start vals

@@

~ add in an option to limit switch back to previous insecticides
~ could add something to put a lower limit on length of rotations

>>>>

~ add in an option to limit switch back to previous insecticides
~ added something to put a lower limit on length of rotations for rwr

@@

~ add option to stop resistance frequencies going below starting value (the thinking being that they could be maintained at this value by selection). It happens in the simulation when there is a cost and the insecticide is not in use.
